Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index

### 2016-01-18 paper.tex
change sampling for test train
references

\usepackage{lipsum}
\usepackage{float}
\usepackage{gensymb}
\usepackage{pdfpages}
\usepackage{listings}

\captionsetup[lstlisting]{labelformat=empty}

\bibliography{thesisrefs}

\title{Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index}
\author{Elle Saber \\ Supervised by Rob J Hyndman \& Di Cook}
\degrees{B.Com.(Hons), Monash University}
\submitdate{November 2015}

@@

\lstset{language=R,
	basicstyle=\scriptsize\ttfamily,
	commentstyle=\ttfamily\color{gray},
	numbers=left,
	numberstyle=\ttfamily\color{gray}\footnotesize,
	stepnumber=1,
	numbersep=5pt,
	backgroundcolor=\color{white},
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	frame=single,
	tabsize=2,
	breaklines=true,
	breakatwhitespace=false,
	title=\lstname,
	escapeinside={},
	keywordstyle={},
	morekeywords={}}
\captionsetup[lstlisting]{labelformat=empty}

\titlepage

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\newpage

\prefacesection{Abstract}

@@

%Graphs, need to redo better
\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/Data/silvan.pdf} 
	\caption{Time series of meterological varibles for Silvan (-37.82, 145.42)} 
	\label{fig:silv} 
\end{figure}

@@

%WS, Temp and FDR contours, see if can change colours to match with the diagram
\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/Data/tw_fdr.pdf} 
	\caption{Wind Speed and temperature coloured by fire danger rating} 
	\label{fig:tw_fdr} 
\end{figure}

@@

\includepdf[pages={1}]{figures/Data/curdist.pdf}

% level plot of GS curing, probably needs resizing
\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/Data/cur_lp.pdf} 
	\caption{Level Plot of Grassland Curing } 
	\label{fig:cur_lp} 
\end{figure}

@@

% level plot of vapour pressure, level plot may be unnesc could just have std plot
\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/Data/vap_ras.pdf} 
	\caption{Raster plot of vapour pressure 9am } 
	\label{fig:vap_ras} 
\end{figure}

@@

%Commented out until final printing, 
%Map of fire ignitions in Victoria
\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/data/firemap.pdf} 
	\caption{Map of fire ignition 2000 - 2009} 
	\label{fig:firemap} 
\end{figure}

%timeseries histogram with count of ignitions per fortnight
\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/data/occurence.pdf} 
	\caption{Number of ignitions by fortnight} 
	\label{fig:occ} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/Data/tw_fire.pdf} 
	\caption{Wind Speed and temperature coloured by fire/no fire} 
	\label{fig:tw_fire} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/Data/dh_fire.pdf} 
	\caption{Drought factor and relative humidity coloured by fire/no fire} 
	\label{fig:dh_fire} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/Data/gv_fire.pdf} 
	\caption{Grassland curing and vapour pressure coloured by fire/no fire} 
	\label{fig:gv_fire} 
\end{figure}

@@

Accuracy is defined as:
\begin{equation}
\label{eq acc}
\text{Accuracy} = \frac{a + d}{a+b+c+d}
\end{equation}

@@

\begin{equation}
\label{eq sens}
\text{Sensitivity} = \frac{a }{a+b}
\end{equation}

\begin{equation}
\label{eq spec}
\text{Specificity} = \frac{d}{c+d}
\end{equation}

\begin{equation}
\label{eq BA}
\text{Balanced Accuracy} = \frac{\frac{a }{a+b} + \frac{d}{c+d} }{2}
\end{equation}

@@

%GAM plots, not sure if this is exactly splines... 
\begin{figure}[h]
\null\vfill\noindent
\includegraphics[page=1,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\hfill
\includegraphics[page=2,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\vfill
\includegraphics[page=3,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\hfill
\includegraphics[page=4,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\vfill
\includegraphics[page=5,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\hfill
\includegraphics[page=6,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\vfill
\null
	\caption{Plots of smoothing functions in Model 4 with 95\% pointwise confident interval} 
	\label{fig:gam_pl} 
\end{figure}

@@

%ROC for logits
\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/all_roc.pdf} 
	\caption{ROC curve for logistic models} 
	\label{fig:ffdi} 
\end{figure}

@@

% Trees with all variables
\begin{figure}[h]
	\centering 
	\includegraphics[page=1, width=1\columnwidth]{figures/trees2.pdf} 
	\includegraphics[page=2, width=1\columnwidth]{figures/trees2.pdf} 
	\caption{Trees with all variables} 
	\label{fig:tree2} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/trees_roc.pdf} 
	\caption{ROC curve for Tree Models} 
	\label{fig:troc} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/varimp.pdf} 
	\caption{Variable Importance for random forest} 
	\label{fig:vimp} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
	\includegraphics[width=1\columnwidth]{figures/roc_rf.pdf} 
	\caption{Variable Importance for random forest} 
	\label{fig:rocrf} 
\end{figure}

@@

\printbibliography

\clearpage

% Appendices start here
\appendix

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/main.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/sort_state.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/new_sort_ncdf.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/convert_coords.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/suburb_list.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/sort_dummy.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/subset_data.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/add_district.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/download_curing.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/download_vapour.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/rainfall.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/add_curing.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/random_testtrain.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/minimax-sampling copy.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/plot_fire.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/plot_weather.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/logistic_output.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/tree.R"}

\lstinputlisting[basicstyle=\tiny]{"/Users/ellesaber/Dropbox/E Saber Honours/Proposal Shared/Rproj/scriptsR/RF_plot.R"}

>>>>

%\usepackage{lipsum}
\usepackage{float}
\usepackage{gensymb}
\usepackage{natbib}
\usepackage{pdfpages}
\usepackage{listings}
\title{Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index}
\author{Elle Saber, Rob J Hyndman \& Di Cook}

@@

\section*{Abstract}

@@

%Graphs, need to redo better
\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/Data/silvan.pdf} 
	\caption{Time series of meterological varibles for Silvan (-37.82, 145.42)} 
	\label{fig:silv} 
\end{figure}

@@

%WS, Temp and FDR contours, see if can change colours to match with the diagram
\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/Data/tw_fdr.pdf} 
	\caption{Wind Speed and temperature coloured by fire danger rating} 
	\label{fig:tw_fdr} 
\end{figure}

@@

%\includepdf[pages={1}]{figures/Data/curdist.pdf}

% level plot of GS curing, probably needs resizing
\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/Data/cur_lp.pdf} 
	\caption{Level Plot of Grassland Curing } 
	\label{fig:cur_lp} 
\end{figure}

@@

% level plot of vapour pressure, level plot may be unnesc could just have std plot
\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/Data/vap_ras.pdf} 
	\caption{Raster plot of vapour pressure 9am } 
	\label{fig:vap_ras} 
\end{figure}

@@

%Commented out until final printing, 
%Map of fire ignitions in Victoria
\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/data/firemap.pdf} 
	\caption{Map of fire ignition 2000 - 2009} 
	\label{fig:firemap} 
\end{figure}

%timeseries histogram with count of ignitions per fortnight
\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/data/occurence.pdf} 
	\caption{Number of ignitions by fortnight} 
	\label{fig:occ} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/Data/tw_fire.pdf} 
	\caption{Wind Speed and temperature coloured by fire/no fire} 
	\label{fig:tw_fire} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/Data/dh_fire.pdf} 
	\caption{Drought factor and relative humidity coloured by fire/no fire} 
	\label{fig:dh_fire} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/Data/gv_fire.pdf} 
	\caption{Grassland curing and vapour pressure coloured by fire/no fire} 
	\label{fig:gv_fire} 
\end{figure}

@@

Accuracy is defined as:
\begin{equation}
\label{eq acc}
\mbox{Accuracy} = \frac{a + d}{a+b+c+d}
\end{equation}

@@

\begin{equation}
\label{eq sens}
\mbox{Sensitivity} = \frac{a }{a+b}
\end{equation}

\begin{equation}
\label{eq spec}
\mbox{Specificity} = \frac{d}{c+d}
\end{equation}

\begin{equation}
\label{eq BA}
\mbox{Balanced Accuracy} = \frac{\frac{a }{a+b} + \frac{d}{c+d} }{2}
\end{equation}

@@

%GAM plots, not sure if this is exactly splines... 
\begin{figure}[h]
\null\vfill\noindent
%\includegraphics[page=1,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\hfill
%\includegraphics[page=2,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\vfill
%\includegraphics[page=3,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\hfill
%\includegraphics[page=4,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\vfill
%\includegraphics[page=5,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\hfill
%\includegraphics[page=6,width=.48\linewidth,height=.45\textheight,keepaspectratio]{figures/gam_pl.pdf}
\vfill
\null
	\caption{Plots of smoothing functions in Model 4 with 95\% pointwise confident interval} 
	\label{fig:gam_pl} 
\end{figure}

@@

%ROC for logits
\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/all_roc.pdf} 
	\caption{ROC curve for logistic models} 
	\label{fig:ffdi} 
\end{figure}

@@

% Trees with all variables
\begin{figure}[h]
	\centering 
%	\includegraphics[page=1, width=1\columnwidth]{figures/trees2.pdf} 
%	\includegraphics[page=2, width=1\columnwidth]{figures/trees2.pdf} 
	\caption{Trees with all variables} 
	\label{fig:tree2} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/trees_roc.pdf} 
	\caption{ROC curve for Tree Models} 
	\label{fig:troc} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/varimp.pdf} 
	\caption{Variable Importance for random forest} 
	\label{fig:vimp} 
\end{figure}

@@

\begin{figure}[h]
	\centering 
%	\includegraphics[width=1\columnwidth]{figures/roc_rf.pdf} 
	\caption{Variable Importance for random forest} 
	\label{fig:rocrf} 
\end{figure}

@@

% Appendices start here
\bibliographystyle{asa}

\bibliography{references}
